---
title: "Figure 2"
author: 'By: Claire Gonzales'
date: "6/13/2022"
output: html_document
---

Figure 2 is a stacked bar plot that show which ocean activities are co-located with eachother from all the publicaitons.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(tidyselect)
library(here)
library(paletteer)
library(ggplot2)
library(forcats)


```


### Reading in Data

Data contains 'orphans'. 

```{r}
mydata <- read_csv(here("data", "Data_total_working_for_r.csv"))
  
```

## Wrangling

First step will be to create a subset of the columns that are required

```{r}
data_sub <- mydata %>% 
  select(id, aquaculture_present, wind_present, wave_present, tidal_present, other_present)
```

Trying to break it up into ocean activities and then creating a co-occurrence matrix within each ocean activity
```{r}
# start with aquaculture

aq <- data_sub %>% 
  filter(aquaculture_present == "1") %>% 
  group_by(aquaculture_present) %>%
  summarize(
   wind = sum(wind_present),
   wave = sum(wave_present),
   tidal = sum(tidal_present),
   other = sum(other_present)
  ) %>% 
  mutate(aquaculture = "0") %>% 
  select(sort(peek_vars())) %>% 
  select(aquaculture, tidal, wave, wind, other)

# now wave

wave <- data_sub %>% 
  filter(wave_present == "1") %>% 
  group_by(wave_present) %>%
  summarize(
    aquaculture = sum(aquaculture_present),
    wind = sum(wind_present),
    tidal = sum(tidal_present),
    other = sum(other_present)
  ) %>% 
  mutate(wave = "0") %>% 
  select(sort(peek_vars())) %>% 
  select(aquaculture, tidal, wave, wind, other)

# now wind

wind <- data_sub %>% 
  filter(wind_present == "1") %>% 
  group_by(wind_present) %>%
  summarize(
    aquaculture = sum(aquaculture_present),
    wave = sum(wave_present),
    tidal = sum(tidal_present),
    other = sum(other_present)
  ) %>% 
  mutate(wind = "0") %>% 
  select(sort(peek_vars())) %>% 
  select(aquaculture, tidal, wave, wind, other)

# now tidal

tidal <- data_sub %>% 
  filter(tidal_present == "1") %>% 
  group_by(tidal_present) %>%
  summarize(
    aquaculture = sum(aquaculture_present),
    wave = sum(wave_present),
    wind = sum(wind_present),
    other = sum(other_present)
  ) %>% 
  mutate(tidal = "0") %>% 
  select(sort(peek_vars())) %>% 
  select(aquaculture, tidal, wave, wind, other)

# and 'other'

other <- data_sub %>% 
  filter(other_present == "1") %>% 
  group_by(other_present) %>%
  summarize(
    aquaculture = sum(aquaculture_present),
    wave = sum(wave_present),
    wind = sum(wind_present),
    tidal = sum(tidal_present)
  ) %>% 
  mutate(other = "0") %>% 
  select(sort(peek_vars())) %>% 
  select(aquaculture, tidal, wave, wind, other)


# 10% manual QC was conducted to confirm that this code works
```

```{r}
## rbind these together and cbind the colnames to them

rownames <- c("aquaculture", "tidal", "wave", "wind", "other")


total <- rbind(aq, tidal, wave, wind, other)

# total_df <- data.frame(cbind(rownames, total))


```

## Make it tidy

```{r}

activity <- as.factor(rep(c("Aquaculture", "Tidal", "Wave", "Wind", "Other"), 5))
buddy <- as.factor(c(rep("Aquaculture", 5), rep("Tidal", 5), rep("Wave", 5), rep("Wind", 5), rep("Other", 5)))

counts <- as.numeric(c(total$aquaculture,
            total$tidal,
            total$wave,
            total$wind,
            total$other))

total_df_tidy <- 
  data.frame(activity, buddy, counts) %>% 
  filter(counts > 0)


# trying to embed levels in the factors so that it will order the way I want it to

total_df_tidy$activity <- factor(total_df_tidy$activity,
                                            levels = c("Aquaculture",
                                                       "Tidal",
                                                       "Wave",
                                                       "Wind",
                                                       "Other"))

total_df_tidy$buddy <- factor(total_df_tidy$buddy,
                                            levels = c("Aquaculture",
                                                       "Tidal",
                                                       "Wave",
                                                       "Wind",
                                                       "Other"))
  

```


## Data Viz

Stacked bar graph using a nice palette and make sure to alphabetize the axes

```{r}
ggplot(data = total_df_tidy, aes(x = activity, y = counts)) +
  geom_bar(position="stack", stat="identity", aes(fill = buddy)) +
  labs(x = "Ocean Activity",
       y = "Count",
       fill = "Co-located Activity") +
  theme_minimal() +
  scale_fill_paletteer_d(palette = "calecopal::bigsur") +
  theme(axis.text.x = element_text(angle = 30))
```



```{r, eval=FALSE, include= FALSE}

# NOTES FROM JULIET on how to fix the ordering problem of the x axis and legend
# "Here Is an example of plot where I did this! It was tricky but you just have to redefine the column in the df with the nested `factors()` and `levels()` functions, then you can keep the code for the ggplot the same, just defining the x axis as the column name as you did before" 

# hist_data_common_name$common_name <- factor(hist_data_common_name$common_name,
#                                             levels = c("red fox",
#                                                        "bobcat",
#                                                        "striped skunk",
#                                                        "raccoon", "rodents",
#                                                        "brush rabbit",
#                                                        "mountain lion",
#                                                        "spotted skunk",
#                                                        "gray fox",
#                                                        "black bear",
#                                                        "opossum"))
# 
# ggplot(hist_data_common_name, aes(x = common_name)) +
#   geom_bar(aes(fill = site)) +
#   ggtitle("Species Occurrence Across Santa Barbara, Summer 2018 - Winter 2019") +
#   xlab("Species") + 
#    ylab("Count") +
#   scale_y_continuous(breaks = seq(00, 250, by = 25)) +
#    theme(panel.background = element_blank(),
#          axis.title.x = element_text(color = "black", face = "bold", size = 15),
#          axis.text.x = element_text(color = "black", size = 10),
#          axis.title.y = element_text(color = "black", face = "bold", size = 15),
#          axis.text.y = element_text(color = "black", size = 12),
#          plot.title = element_text(color="black", size = 11, face = "bold"),
#          panel.border = element_rect(colour = "black", fill = NA, size = 2)) +
#   scale_fill_brewer(palette = c("Set2"))
```

