---
title: "Figure 1 script"
author: 'By: Claire Gonzales'
date: "6/9/2022"
output: 
  html_document: 
    theme: lumen
    code_folding: hide
---

### Description

**OBJECTIVE**: Figure 1 is going to be two panes. The first pane (Fig. 1a) will have total publications published over time. The second pane (Fig. 1b) will have three lines (ecology, governance, and socioeconomics) and will show the frequency of these types of publications over time. All three categories in pane 2 (Fig. 1b) will not add up to the total publications in pane 1 (Fig. 1a).

**REFLECTIONS**: I'm trying to figure out if these visualizations are useful and informative. I think the story that they tell is that socioeconomics tends to be the leading discipline in current co-location literature. It makes sense for governance to be lower because policy pathways aren't yet established for co-location in most regions so there's isn't much to study in that discipline. However, ecology should be higher. In fact, we saw a widespread lack of ecological metrics, even in those publications that clearly were referring to the ecology of co-location. Call to action: future research should fill this gap. Not only do we need to collect baseline metrics when publishing co-location studies, but we also need to begin measuring environmental impacts from co-location activities, which has largely not been addressed.


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(here)
library(lubridate)
library(plotly)
library(paletteer)
library(cowplot)

```

### Reading in Data

Data contains 'orphans'. 

```{r}
mydata <- read_csv(here("data", "Data_total_working_for_r.csv"))
  
```

### Pane 1 Wrangling
Subset to only look at year and types of co-location. 

```{r}
data_sub <- mydata %>% 
  select(first_author, year, ecology, governance, socioecon) %>% 
  group_by(year) %>% 
  summarize(count = n())

```

### Pane 1 Viz
```{r}
# Pane 1 (Fig. 1a)
# count of publications over time

g1 <- ggplot(data = data_sub, aes(x = year, y = count)) +
  geom_line(color = "darkgray", size = .7) +
  labs(x = "Year",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45))

ggplotly(g1)
```

### Pane 2 Wrangling

This might be semi sloppy code and there might be a cleaner way to do this but I'm not sure what that would be and I feel confident in the messy coding I've done here. 
```{r}
# Need to rearrange the data for pane 2
# Plan to create a subset that filters for all the ecology counts and totals them over time
  # then do the same thing for governance and socioecon
  # then rbind them together

data_sub_b_ecol <- mydata %>% 
  select(first_author, year, ecology) %>% 
  group_by(year) %>% 
  summarize(count = sum(ecology))

ecology <- rep(c("Ecology"), times = 12)

#colnames <- c("year", "discipline", "count")

ecol_sub <- cbind(data_sub_b_ecol$year,
              ecology,
              data_sub_b_ecol$count)

ecol_df <- data.frame(ecol_sub) %>% 
  rename(year = V1) %>% 
  rename(discipline = ecology) %>% 
  rename(count = V3)
```

```{r}
# same thing for socioeconomics section
data_sub_b_socio <- mydata %>% 
  select(first_author, year, socioecon) %>% 
  group_by(year) %>% 
  summarize(count = sum(socioecon))

socioecon <- rep(c("Socioeconomics"), times = 12)

#can use the colnames value from above

socio_sub <- cbind(data_sub_b_socio$year,
              socioecon,
              data_sub_b_socio$count)

socio_df <- data.frame(socio_sub) %>% 
  rename(year = V1) %>% 
  rename(discipline = socioecon) %>% 
  rename(count = V3)

```

```{r}
# same thing for governance section
data_sub_b_gov <- mydata %>% 
  select(first_author, year, governance) %>% 
  group_by(year) %>% 
  summarize(count = sum(governance))

governance <- rep(c("Governance"), times = 12)

#can use the colnames value from above

gov_sub <- cbind(data_sub_b_gov$year,
              governance,
              data_sub_b_gov$count)

gov_df <- data.frame(gov_sub) %>% 
  rename(year = V1) %>% 
  rename(discipline = governance) %>% 
  rename(count = V3)
```

```{r}
# rbinding the 3 dfs into one

all_df <- rbind(ecol_df, gov_df, socio_df) %>% 
  mutate(year = as.numeric(year)) %>% 
  mutate(count = as.integer(count))

# class was checked and its a data frame

```

### Pane 2 Viz

Using ggplotly() here to allow us to look at each value, when needed. 

```{r}
g2 <- ggplot(data = all_df, aes(x = year, y = count)) +
  geom_line(aes(color = discipline), size = .7) +
  labs(x = "Year",
       y = "Count") +
  theme_minimal() +
  theme(legend.title = element_blank(), legend.position= 'bottom', axis.text.x = element_text(angle = 45)) +
  scale_colour_manual(values = c("Ecology" = "#00BA38", "Governance" = "#619CFF", "Socioeconomics" = "#F8766D"))

ggplotly(g2)
```

### Patching panes together

Using cowplot package and `plot_grid()` to patch panes 1 and 2 together

```{r}
plot_grid(g1, g2, labels = c("A", "B"))

# ggsave(filename = here("figures", "fig1.jpeg"), width = 7, height = 4, units = "in")

```

**Figure 1.** Shows frequency of publications over time (years 2000-2020). **Pane A** reflects the total frequency of co-location publications published over time. **Pane B** reflects the frequency of co-location publications, separated by publication discipline (ie ecology, governance or socioeconomics), published over time.  
