---
title: "Figure 3 script"
author: 'By: Claire Gonzales'
date: '2022-06-17'
output: 
  html_document: 
    theme: lumen
    code_folding: hide
---

### Description

**OBJECTIVE**: This will be a spatial visualization of where co-location is being considered. Current plan is to use R to only create the data frame that we need and then use tableau to create the visualization (hopefully.)


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

library(tidyverse)
library(here)
library(paletteer)
library(ggplot2)

```


### Reading in Data

Data contains 'orphans'. 

```{r}
mydata <- read_csv(here("data", "Data_total_working_for_r.csv"))
  
```

### Wrangling

We have figured out the code for this section a couple months ago in the lme_code.Rmd script to put the necessary lme data into tidy format.

```{r}
lme_clean <- mydata %>% 
  select(id, lme1, lme2, lme3, lme4, lme5, lme6)

lme_tidy <- lme_clean %>% 
  gather("df", "lme", 2:7, na.rm = TRUE) %>% # output at this stage was QC'd to make sure that the code worked (it did!)
  group_by(lme) %>% 
  summarize (
    count = n()
  )

# this output shows each lme (by name) and how many times that lme is referenced in the literature. North Sea far in the lead, being mentioned 34 times. 

# > class(lme_tidy$lme)
# [1] "character"
# > class(lme_tidy$count)
# [1] "integer"

# classes might have to be changed to factor and numeric in future
```

```{r}
write.csv(lme_tidy, here("data", "lme_tidy.csv"))
```

### Tableau Viz

Tableau figure can be found here: https://public.tableau.com/app/profile/claire.gonzales/viz/synthesis_figure3/Sheet3

Honestly, I don't love it? I feel like it falls a little flat.

### R Viz

I am going to try my hand at an r visualization using `geom_sf` to see if I can create something a little better that way.

```{r}
# install.packages(c("cowplot", "googleway", "ggplot2", "ggrepel", "ggspatial", "libwgeom", "sf", "rnaturalearth", "rnaturalearthdata"))

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
```

Let's load some data.
```{r}

world <- ne_countries(scale = "medium", returnclass = "sf") 
# this provides a map of countries of the entire world. Use ne_countries to pull country data and choose the scale

locations <- read_csv(here("data", "lme_tidy_location.csv"))
# this is the locations of the lmes (not a shapefile)

```

And now try to make a preliminary map
```{r}
ggplot(data = world) +
  geom_sf() +
  geom_point(data = locations, aes(x = long, y = lat, size = count), shape = 23, fill = "darkred")
```

