---
title: "Initial graphs"
author: 'By: Claire Gonzales'
date: "2/7/2022"
output: 
  html_document: 
    theme: lumen
---

### Overveiw

This document will outline initial visualizations from co-location synthesis data. Inital questions that this data will attempt to address are as follows:

- Is co-location research being conducted?
- Where is it being conducted?
- What are initial areas of opportunity being highlighted in the literature?
- What are some potential obstacles being highlighted in the literature? 


```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)

library(tidyverse)
library(here)
library(lubridate)
```

### Reading in Data

```{r}

mydata <- read_csv(here("data", "Data_total_working_for_r.csv"))
  
```

### Data subset

Subset to only look at year and types of co-location. 

```{r}
data_sub1 <- mydata %>% 
  select(first_author, year, country, aquaculture_present, wind_present, wave_present, tidal_present, other_present)

ggplot(data = data_sub1, aes(x = year)) +
  geom_histogram(binwidth = 1) +
  theme_minimal()
```

